Verifying Demonstrations

### 2019-02-19 paper/adversary-model.tex
Adapts adversary figure to only one adversary

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the in-system adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data as a function \(d\) of the protest and protester, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{in-system-adversary}).
  }
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the adversary model.
    The protester (with real identity) \(P\) and witness (with real identity) 
    \(W\) communicate.
    They exchange protocol data as a function~\(d\) of the protest and 
    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
    \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the 
    adversary.
  }
\end{figure}
